---
title: "Data_Mining Homework 3"
author: "Matthew Borelli"
date: "4/14/2020"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'D:/Documents/MA Econ/Spring/Data Mining and Statistical Learning/ECO-395M-Homework-3/data')

library(dplyr)
library(plyr)
library(ggplot2)
library(randomForest)
library(stargazer)
```

# Predictive Model Building

```{r green_data, include=FALSE}
green = read.csv("./greenbuildings.csv")
```

## Introduction

There has been an increased focus on creating environmentally conscious buildings, also known as green buildings, which adds a wrinkle into the already complex decision-making process for commercial real estate firms on what types of buildings they should construct. There are a variety of potential benefits that could make investing in constructing green buildings a worthwhile decision:

 - Lower operational costs (water, climate control, waste management, etc.).
 - Better indoor environments (natural sunlight for instance) could encourage better productivity and lead to happier and more motivated employees, increasing the incentives for a business to rent out those spaces.
 - Increased PR for both the real estate firm and the business renting the space due to positive public perceptions of green buildings.
 - Green buildings potentially have longer lives of operation. They are both physically constructed to last longer and less susceptible to energy market shocks.
 
 While this list of benefits seems to make an airtight case for commercial real estate firms to fully switch to constructing green buildings, there is a major issue. Green buildings are generally more costly for these firms to construct as a result of the standards that must be met in order to achieve green building certification from LEED or EnergyStar. However, as described above, it is possibly true that business would be willing to pay hire rents for office space in green buildings. This "Green Premium" would increase the profit incentives for commercial real estate firms to construct green buildings, which could be considered a societal good. However, we can't be certain that the "Green Premium" exists, or if so to what degree having a green certified building would increase rent prices. This analysis has two main goals:
 
 1. Create the best predictive model possible for rent prices.
 2. Use said model to quantify the average change in rental income per sq. ft. associated with attaining green certification, holding any other features of the building constant.
 
 Completing these two goals will give us a tool that we can employ to predict rent prices for buildings given certain features, as well as demonstrate to commercial real estate firms whether attempting to focus future constructions projects on green buildings is financially worth it. Given the uncertainty of the potential positive features listed above, this is a good quantifiable method for providing evidence for or against the impact of green certification on these companies' decision making processes.
 
## Data and Model

For this analysis, we are using using a data set of 7894 commercial rental properties in the U.S. Of these, 695 are certified as green buildings through either LEED or EnergyStar. In this data set, each green building is matched with a cluster of nearby non-green commercial buildings. Data is collected for a variety of features about the buildings, including rent in dollars per square foot, total square footage, age of building, etc. We will use these features in order to best predict building prices and quantify how much of a "Green Premium" exists. To start, we want to first look at a summary of the differences between different green classifications to give us a reference point for future results.

```{r green_summary, echo=FALSE}
summary_green_1 = as.data.frame(ddply(green, c("LEED", "Energystar"), summarise,
                                   N = length(Rent),
                                   "Rent" = mean(Rent),
                                   "Leasing Rate" = mean(leasing_rate),
                                   "Age" = mean(age),
                                   "Class A %" = round(mean(class_a)*100, 2),
                                   "Class B %" = round(mean(class_b)*100, 2)))
summary_green_1

summary_green_2 = as.data.frame(ddply(green, c("LEED", "Energystar"), summarise,
                                   "Temp Control Days" = mean(total_dd_07),
                                   "% w/ Amenities" = round(mean(amenities)*100, 2),
                                   "Precipitation" = mean(Precipitation)))
summary_green_2

summary_green_3 = as.data.frame(ddply(green, c("LEED", "Energystar"), summarise,
                                   "Gas Costs" = mean(Gas_Costs),
                                   "Electricity Costs" = mean(Electricity_Costs)))
summary_green_3
```

There are a lot of observations to make from these summary tables. A simple glance at the rent column shows that rent appears to be higher in green certified buildings than in non-green certified buildings. However, there also seems to be a big difference in the rental rate between EnergyStar certified buildings and LEED certified buildings, `r (summary_green_1[2,4] - summary_green_1[3,4])`$ per square foot. Looking closer at these tables, there are large differences in feature variables amongst the different populations of building types. The starkest difference is in days of temperature control, defined as the number of days where the building needs heating or cooling. EnergyStar buildings need `r (summary_green_2[1,3] - summary_green_2[2,3])` days fewer of heating or cooling than buildings with no green certification, but LEED buildings actually need `r (summary_green_2[3,3] - summary_green_2[1,3])` days more. 

These differences necessitate more formal evaluations of the data. Particularly, we will evaluate the effect of certification separately for LEED and EnergyStar, as buildings that meet their respective certifications seem to have different standards. To predict building rent prices  we will utilize random forest regression  First, we split the data into training and testing data, then use random forests to pick the model with the lowest error. For robustness, we will test the error for different numbers of trees in the random forest. However, we can't use random forests to quantify the effect of green certification on rent prices, as large tree and forests are generally not interpretable in the way we want. Therefore, we will utilizeTo check robustness, we will compare the simple model of rent regressed onto green certification with the model identified through our selection process on out-of-sample performance.


## Results

### Random Forest Model Errors
```{r green_forest_eval, include=FALSE}
# Setting a seed for consistent results
set.seed(14)

# Establish Train/Test split
N = nrow(green)
train_frac = 0.8
N_train = floor(train_frac*N)
N_test = N - N_train
train_ind = sample.int(N, N_train, replace=FALSE) %>% sort
green_train = green[train_ind,]
green_test = green[-train_ind,]

# Random Forest
forest_green = randomForest(Rent ~ size + leasing_rate + stories + age + renovated + class_a + class_b + LEED + Energystar + LEED*Energystar + net + amenities + total_dd_07 + Precipitation + Gas_Costs + Electricity_Costs, mtry=1, nTree=100, data=green_train)
plot(forest_green)

```
The model errors are high at low amounts of trees, flattening out at around 100 trees, so we will use 100 trees in our random forest model.

### Variable Importance Plot

Random Forests, as well as other large tree regression methods, are generally not interpretable. However, we can create measures of variable importance to help understand which feature variables by looking at which variables best improve error within the aggregated trees. Below is a variable importance plot, ranked in order of importance.

```{r, importance}
varImpPlot(forest_green)
```

The most important variables are closely related since electricity costs, total days of heating or cooling required, precipitation amounts, and gas costs are all related to the running costs of a building. Interestingly, the least important variables are the green certification dummy variables, with EnergyStar being slightly more important than LEED. This is evidence that having certification as a green building doesn't have a large impact on rental rates, but to be sure we will now check using stepwise regression model selection.

### Green Premium

To start the stepwise selection process, we introduce a null model of rent regressed onto the green building certification variables.

```{r simple_green_model}
simple_green = glm(Rent ~ LEED + Energystar + Energystar*LEED, data=green)
stargazer(simple_green, type="text")
```

In this regression, we get positive coefficients for each of the green certification variables, but only EnergyStar certification's effect is statistically significant. LEED does not have any significantly positive effect on rent in our simple model. To compare, the following is the model picked by stepwise selection using AIC as the loss function.

```{r green_step, echo=FALSE}
green_step = step(simple_green, 
			scope=~(. + size + leasing_rate + stories + age + renovated + class_a + class_b + net + amenities + total_dd_07 + Precipitation + Gas_Costs + Electricity_Costs)^2)

library(finalfit)
explanatory = c("LEED", "Energystar", "green_rating")
dependent = 'Rent'
green %>%
  finalfit(dependent, explanatory)


```

## Conclusion

In the future, it would be prudent to access data that distinctifies the specific rating levels for LEED and EnergyStar green certification.

# What Causes What?

## 1.

## 2.

## 3.

## 4.


# Clustering and PCA

```{r wine_data, include=FALSE}
wine = read.csv("./wine.csv")
```

## Introduction

## Data and Model

## Results

## Conclusion

# Market Segmentation

```{r social_data, include=FALSE}
social = read.csv("./social_marketing.csv")
```

## Introduction

## Data and Model

## Results

## Conclusion

